---
title: "week 6"
output: html_document
---

# Chapter 7 Classification

- A regression model predicts a numeric or continuous value.

- A classification model predicts a class label or group membership.

```{r}
library(tidyverse)
complaints <- read_csv("complaints.csv")
```


```{r}
glimpse(complaints)
```

```{r}
head(complaints$`Consumer complaint narrative`)
```

XXXX are used to protect personally identifiable information

# 7.1.1 Building our first classification model

```{r}
library(tidymodels)

set.seed(1234)
complaints2class <- complaints %>%
  mutate(product = factor(if_else(
    Product == paste("Credit reporting, credit repair services,",
                     "or other personal consumer reports"),
    "Credit", "Other"
  )))

# split data into training data and testing data
complaints_split <- initial_split(complaints2class, strata = product)

complaints_train <- training(complaints_split)
complaints_test <- testing(complaints_split)
```

```{r}
dim(complaints_train)
```

```{r}
dim(complaints_test)
```

```{r}
complaints_rec <-
  recipe(product ~ `Consumer complaint narrative`, data = complaints_train)
```

```{r}
library(textrecipes)

complaints_rec <- complaints_rec %>%
  step_tokenize(consumer_complaint_narrative) %>%
  # keep the 1000 most frequent tokens
  step_tokenfilter(consumer_complaint_narrative, max_tokens = 1e3) %>%
  # compute tf-idf
  step_tfidf(consumer_complaint_narrative)
```

```{r}
complaint_wf <- workflow() %>%
  add_recipe(complaints_rec)
```

```{r}
library(discrim)
nb_spec <- naive_Bayes() %>%
  set_mode("classification") %>%
  set_engine("naivebayes")

nb_spec
```

# add the naive Bayes model to the workflow

```{r}
nb_fit <- complaint_wf %>%
  add_model(nb_spec) %>%
  fit(data = complaints_train)
```

# 7.1.2 Evaluation
```{r}
# create 10-fold cross-validation sets, and use these resampled sets for performance estimates.
set.seed(234)
complaints_folds <- vfold_cv(complaints_train)

complaints_folds
```

```{r}
nb_wf <- workflow() %>%
  add_recipe(complaints_rec) %>%
  add_model(nb_spec)

nb_wf
```

```{r}
nb_rs <- fit_resamples(
  nb_wf,
  complaints_folds,
  control = control_resamples(save_pred = TRUE)
)
```

# extract the relevant information using collect_metrics() and collect_predictions()
```{r}
nb_rs_metrics <- collect_metrics(nb_rs)
```


```{r}
nb_rs_predictions <- collect_predictions(nb_rs)
```

```{r}
nb_rs_metrics
```

ROC curve shows how well a classification model can distinguish between classes,

```{r}
nb_rs_predictions %>%
  group_by(id) %>%
  roc_curve(truth = product, .pred_Credit) %>%
  autoplot() +
  labs(
    color = NULL,
    title = "ROC curve for US Consumer Finance Complaints",
    subtitle = "Each resample fold is shown in a different color"
  )
```

The area under each of these curves is the roc_auc metric we have computed. If the curve was close to the diagonal line, then the model’s predictions would be no better than random guessing.

```{r}
# plot confusion matrix
conf_mat_resampled(nb_rs, tidy = FALSE) %>%
  autoplot(type = "heatmap")
```

7.3 Compare to a lasso classification model

## create lasso regression

```{r}
lasso_spec <- logistic_reg(penalty = 0.01, mixture = 1) %>%
  set_mode("classification") %>%
  set_engine("glmnet")

lasso_spec

lasso_wf <- workflow() %>%
  add_recipe(complaints_rec) %>%
  add_model(lasso_spec)

lasso_wf
```

## turning lasso regression parameter
tune() can be treated as a placeholder for the regularization penalty.
```{r}
tune_spec <- logistic_reg(penalty = tune(), mixture = 1) %>%
  set_mode("classification") %>%
  set_engine("glmnet")

tune_spec
```

turn the parameter
```{r}
tune_wf <- workflow() %>%
  add_recipe(complaints_rec) %>%
  add_model(tune_spec)

set.seed(2020)
tune_rs <- tune_grid(
  tune_wf,
  complaints_folds,
  grid = lambda_grid,
  control = control_resamples(save_pred = TRUE)
)

tune_rs
```

```{r}
collect_metrics(tune_rs)
```

# view the results and select the best model
```{r}
tune_rs %>%
  show_best("roc_auc")

chosen_auc <- tune_rs %>%
  select_by_one_std_err(metric = "roc_auc", -penalty)

final_lasso <- finalize_workflow(tune_wf, chosen_auc)
```

# Case study: sparse encoding
The computational engine can be more efficient when text data is transformed to a sparse matrix

```{r}
library(hardhat)
sparse_bp <- default_recipe_blueprint(composition = "dgCMatrix")

sparse_wf <- workflow() %>%
  add_recipe(complaints_rec, blueprint = sparse_bp) %>%
  add_model(tune_spec)

sparse_wf
```

# including non-text data

```{r}
more_vars_rec <-
  recipe(product ~ date_received + tags + consumer_complaint_narrative,
         data = complaints_train)

more_vars_rec <- more_vars_rec %>%
  # extract the month and day of the week
  step_date(date_received, features = c("month", "dow"), role = "dates") %>%
  step_rm(date_received) %>%
  # convert the new month and day-of-the-week columns to indicator variables
  step_dummy(has_role("dates"))
```

It is possible with many data sets to achieve high accuracy just by predicting the majority class all the time, but such a model is not useful in the real world. Accuracy alone is often not a good way to assess the performance of classification models.


Chapter 8 Dense neural networks
```{r}
library(tidyverse)

kickstarter <- read_csv("data/kickstarter.csv.gz")
kickstarter
```

Documents that are longer than this length are truncated (information is thrown away), and documents that are shorter than this length are padded with zeroes (an empty, non-informative value) to get to the chosen sequence length. This sequence length is a hyperparameter of the model.

Preprocessing
```{r}
library(textrecipes)

max_words <- 2e4
max_length <- 30

kick_rec <- recipe(~ blurb, data = kickstarter_train) %>%
  step_tokenize(blurb) %>%
  step_tokenfilter(blurb, max_tokens = max_words) %>%
  step_sequence_onehot(blurb, sequence_length = max_length)

kick_rec
```

#  One-hot sequence embedding of text

When using step_sequence_onehot() each word is assigned an integer index, and the sequence of tokens is replaced with the corresponding indices. 
```{r}
# transforms tokens into a numeric format appropriate for modeling
recipe(~ text, data = small_data) %>%
  step_tokenize(text) %>%
  step_sequence_onehot(text, sequence_length = 6, prefix = "",
                       padding = "pre", truncating = "post") %>%
  prep() %>%
  bake(new_data = NULL, composition = "matrix")
```

# Building simple flatten dense network
```{r}
library(keras)
# initialize keras model sequential
dense_model <- keras_model_sequential() %>%
  layer_embedding(input_dim = max_words + 1,
                  output_dim = 12,
                  input_length = max_length) %>%
  layer_flatten() %>%
  layer_dense(units = 32, activation = "relu") %>%
  layer_dense(units = 1, activation = "sigmoid")

```

# define compile for model
```{r}
dense_model %>% compile(
  optimizer = "adam",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)
```

# fit model
```{r}
dense_history <- dense_model %>%
  fit(
    x = kick_train,
    y = kickstarter_train$state,
    batch_size = 512,
    epochs = 20,
    validation_split = 0.25,
    verbose = FALSE
  )
```

# visualize the results
```{r}
plot(dense_history)
```

# Evaluation
create validation split from the training set
```{r}
set.seed(234)
kick_val <- validation_split(kickstarter_train, strata = state)
kick_val
```

# get prediction result

```{r}
val_res <- keras_predict(dense_model, kick_assess, state_assess)
val_res
```

# Using pre-trained word embeddings
```{r}
library(textdata)
# obtain glove embedding
glove6b <- embedding_glove6b(dimensions = 50) %>% select(1:13)
glove6b
```

#  LSTM model

# preprocessing the data
```{r}
library(textrecipes)

max_words <- 2e4
max_length <- 30

kick_rec <- recipe(~ blurb, data = kickstarter_train) %>%
  step_tokenize(blurb) %>%
  step_tokenfilter(blurb, max_tokens = max_words) %>%
  step_sequence_onehot(blurb, sequence_length = max_length)

kick_prep <- prep(kick_rec)
kick_train <- bake(kick_prep)
```

# create LSTMs
```{r}
library(keras)

lstm_mod <- keras_model_sequential() %>%
  layer_embedding(input_dim = max_words + 1, output_dim = 32) %>%
  layer_lstm(units = 32) %>%
  layer_dense(units = 1, activation = "sigmoid")

lstm_mod
```

# set up complile
```{r}
lstm_mod %>%
  compile(
    optimizer = "adam",
    loss = "binary_crossentropy",
    metrics = c("accuracy")
  )
```

# fit the model
```{r}
lstm_history <- lstm_mod %>%
  fit(
    kick_train,
    kickstarter_train$state,
    epochs = 10,
    # set apart a fraction of the training data for evaluation and assessment.
    validation_split = 0.25,
    batch_size = 512,
    verbose = FALSE
  )

lstm_history
```

# visulize the performance
```{r}
plot(lstm_history)
```

# Evaluation

```{r}
set.seed(234)
kick_val <- validation_split(kickstarter_train, strata = state)
kick_val

kick_analysis <- bake(kick_prep, new_data = analysis(kick_val$splits[[1]]),
                      composition = "matrix")
```

# we can use dropout to prevent overfitting
```{r}
# fit data to validation set
lstm_mod <- keras_model_sequential() %>%
  layer_embedding(input_dim = max_words + 1, output_dim = 32) %>%
  layer_lstm(units = 32, dropout = 0.4, recurrent_dropout = 0.4) %>%
  layer_dense(units = 1, activation = "sigmoid")

lstm_mod %>%
  compile(
    optimizer = "adam",
    loss = "binary_crossentropy",
    metrics = c("accuracy")
  )

val_history <- lstm_mod %>%
  fit(
    kick_analysis,
    state_analysis,
    epochs = 10,
    validation_data = list(kick_assess, state_assess),
    batch_size = 512,
    verbose = FALSE
  )

val_history
```

# evalute performance of the model in validation set
```{r}
val_res <- keras_predict(lstm_mod, kick_assess, state_assess)
val_res %>% metrics(state, .pred_class, .pred_1)
```

# bidirectional LSTM

```{r}
bilstm_mod <- keras_model_sequential() %>%
  layer_embedding(input_dim = max_words + 1, output_dim = 32) %>%
  bidirectional(layer_lstm(units = 32, dropout = 0.4,
                           recurrent_dropout = 0.4)) %>%
  layer_dense(units = 1, activation = "sigmoid")

bilstm_mod %>%
  compile(
    optimizer = "adam",
    loss = "binary_crossentropy",
    metrics = c("accuracy")
  )

bilstm_history <- bilstm_mod %>%
  fit(
    kick_analysis,
    state_analysis,
    epochs = 10,
    validation_data = list(kick_assess, state_assess),
    batch_size = 512,
    verbose = FALSE
  )

bilstm_history
```

# stacking LSTM layers
stacking LSTM can increase the ability of a network to represent the data well.
```{r}
stacked_mod <- keras_model_sequential() %>%
  layer_embedding(input_dim = max_words + 1, output_dim = 32) %>%
  layer_lstm(units = 32, dropout = 0.4, recurrent_dropout = 0.4,
             return_sequences = TRUE) %>%
  layer_lstm(units = 32, dropout = 0.4, recurrent_dropout = 0.4) %>%
  layer_dense(units = 1, activation = "sigmoid")
```

# 
